Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-18 edubots_surveys.Rnw

% Describe the survey and population
We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} %in Fig. \ref{figure:teachers_population}
) and 205 for the second one (\textit{survey2}). The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively. Regarding gender, 61\% of the teachers were male and 32\% female (approximately 5\% chose not to disclose it). Finally, the responses are equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.

@@

A question in the survey was also focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class. The 282 

>>>>

% Describe the survey and population
We collected responses from 282 teachers from Spain and Spanish Speaking countries for the first survey (\textit{survey1} and 205 for the second one (\textit{survey2}). The two forms were open for approximately the same amount of time, around two months. The sample includes mostly teachers from university, although about 32\% and 8\% are from vocational education in the first and second survey respectively. Regarding gender, 61\% of the teachers were male and 32\% female, while approximately 5\% chose not to disclose it. Finally, the responses are more or less equally distributed according to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 26\% for 6-15 years of experience, 30\% for 16-25, and 20\% for teachers with more than 25 years of experience.

@@

Some of the questions in the survey were focused on the impact of the COVID19 pandemic between 2020 and 2021, in the teachers' viewpoints towards the use of instant messaging apps int their class. Our main intention in this case was to assess whether a crisis will bring about some kind of change in the use of tools.
The 282 
